---
title: "Grouping and Summarizing"
author: "Suzanne Childress"
date: "1/7/2021"
output:
  html_document:
    highlight: textmate
    theme: cosmo
  pdf_document: default
---


Usually when working with data, we want to aggregate it to extract meaning. The most common ways to aggregate are to count, sum, min or max.


```{r, eval=FALSE}
# Let's count the records in our data.

rest_df_count <- rest_df %>% count()

# Now let's count the number of observations for each restaurant.

rest_df_count2 <- rest_df %>% count(NAME)

rest_df %>% count(NAME,sort=TRUE)

```

Many times we need to sum data.
summarise() creates a new data frame. It will have one (or more) rows for each combination of grouping variables; if there are no grouping variables, the output will have a single row summarising all observations in the input. It will contain one column for each grouping variable and one column for each of the summary statistics that you have specified.

```{r, eval=FALSE}
# Let's sum the inspection scores.

rest_df %>% summarize(total_points=(sum(SCORE_INSPECTION, na.rm=TRUE)))

```

Frequently we also want to group data and summarize it:


```{r, eval=FALSE}
# Let's sum the inspection scores.

rest_df %>% group_by(NAME)%>%summarize(rest_points=(mean(SCORE_INSPECTION, na.rm=TRUE)))

```



